---
title: "Project"
output: html_document
date: "2024-04-19"
---

```{r}
library(AER)
library(plm)
```

### Export

```{r}
data <- read.csv("df_export.csv")
head(data)
```

Let's build Fixed Effects Model. On this model logarithm of units of pet food sold is the independent variable.

```{r}
model_fixed <- plm(log(export_volume_units) ~ war + price, data = data, index = c('observation', 'time.period'), model="within")
summary(model_fixed)
```

Let's try to male the increase of units sold as our independent variable.

```{r}
model1 <- plm(units_increase ~ war + price, data = data, index = c('observation', 'time.period'), model="within")
summary(model1)
```

Now let's build a Random Effects Model.

```{r}
model_random <- plm(log(export_volume_units) ~ 
                      war + price + export_volume_tons + 
                      category_dry_cats_and_dogs +
                      category_treats + pet_type_cats +
                      price_segment_economy + price_segment_middle +
                      package_type_pouch, 
                      data = data, index = c('observation', 'time.period'), model="random")
summary(model_random)
```

To determine which method among Fixed Effect Model and Random Effects model is better, the authors used Hausman test. The appropriate model for the project data is **Random Effects Model**.

```{r}
phtest(model_fixed,model_random)
```

The next step was to choose appropriate variables. As the model contains a lot of dummy variables, it is convenient to test joint significance of each group of these binary variables. For such task, in Random Effects Model, Mulivariate Wald test is used.

```{r}
wald_result <- waldtest(model_random, c('category_dry_cats_and_dogs', 'category_treats'))
print(wald_result)
```

```{r}
model_random2 = plm(log(export_volume_units) ~ 
                      war + price + export_volume_tons + 
                      pet_type_cats + price_segment_economy + 
                      price_segment_middle + package_type_pouch, 
                      data = data, index = c('observation', 'time.period'), model="random")
summary(model_random2)
```

Dropping export_volume_tons from the model.

```{r}
model_random3 = plm(log(export_volume_units) ~ 
                      war + price + pet_type_cats + 
                      price_segment_economy + 
                      price_segment_middle + package_type_pouch, 
                      data = data, index = c('observation', 'time.period'), model="random")
summary(model_random3)
```

```{r}
xnames <- c()
wald_result <- waldtest(model_random3, c('price_segment_economy', 'price_segment_middle'))
print(wald_result)
```

Here is the final model.

```{r}
final_model_random = plm(log(export_volume_units) ~ 
                      war + price + pet_type_cats + package_type_pouch, 
                      data = data, index = c('observation', 'time.period'), model="random")
summary(final_model_random)
```

```{r}
phtest(model_fixed, final_model_random)
```

```{r}
final_model_random = plm(units_increase ~ 
                      war + price + pet_type_cats + package_type_pouch, 
                      data = data, index = c('observation', 'time.period'), model="random")
summary(final_model_random)
```

## INTERNAL MARKET

Let's do the same or the internal market.

```{r}
data_internal <- read.csv("df_internal.csv")
head(data_internal)
```

Let's build a Random Effects Model.

```{r}
model_random_internal <- plm(log(volume_units) ~ volume_tons + war + price + category_dry_cats_and_dogs + category_treats + manufacturer_PP_Hal_Euro_Contract+ manufacturer_TOV_KORMOTECH + manufacturer_TOV_PTF_TECHNO + pet_type_cats + price_segment_economy + price_segment_middle + package_type_can + package_type_glass_jar + package_type_pack + package_type_pouch, data = data_internal, index = c('observation', 'time.period'), model="random")
summary(model_random_internal)
```

```{r}
wald_result <- waldtest(model_random_internal, c('manufacturer_PP_Hal_Euro_Contract',                                   'manufacturer_TOV_KORMOTECH', 'manufacturer_TOV_PTF_TECHNO'))
print(wald_result)
```

```{r}
model_random_internal <- plm(log(volume_units) ~ volume_tons + war + price + category_dry_cats_and_dogs + category_treats + pet_type_cats + price_segment_economy + price_segment_middle + package_type_can + package_type_glass_jar + package_type_pack + package_type_pouch, data = data_internal, index = c('observation', 'time.period'), model="random")
summary(model_random_internal)
```

Dropping price_segment_economy. Economy&premium is the base group now.

```{r}
model_random_internal <- plm(log(volume_units) ~ volume_tons + war + price + category_dry_cats_and_dogs + category_treats + pet_type_cats + price_segment_middle + package_type_can + package_type_glass_jar + package_type_pack + package_type_pouch, data = data_internal, index = c('observation', 'time.period'), model="random")
summary(model_random_internal)
```

```{r}
model_random_internal <- plm(log(volume_units) ~ volume_tons + war + category_dry_cats_and_dogs + category_treats + pet_type_cats + price_segment_middle + package_type_can + package_type_glass_jar + package_type_pack + package_type_pouch, data = data_internal, index = c('observation', 'time.period'), model="random")
summary(model_random_internal)
```

The same for increase in units:

```{r}
model_random_internal <- plm(units_increase ~ volume_tons + war + price + category_dry_cats_and_dogs + category_treats + manufacturer_PP_Hal_Euro_Contract+ manufacturer_TOV_KORMOTECH + manufacturer_TOV_PTF_TECHNO + pet_type_cats + price_segment_economy + price_segment_middle + package_type_can + package_type_glass_jar + package_type_pack + package_type_pouch, data = data_internal, index = c('observation', 'time.period'), model="random")
summary(model_random_internal)
```

As we can see, the only significant variable is war. So let's consider the Fixed Effects Model.

```{r}
model_fixed_internal <- plm(units_increase ~ volume_tons + war + price + category_dry_cats_and_dogs + category_treats + manufacturer_PP_Hal_Euro_Contract+ manufacturer_TOV_KORMOTECH + manufacturer_TOV_PTF_TECHNO + pet_type_cats + price_segment_economy + price_segment_middle + package_type_can + package_type_glass_jar + package_type_pack + package_type_pouch, data = data_internal, index = c('observation', 'time.period'), model="within")
summary(model_fixed_internal)
```

And conduct Hausman Test to choose between Fixed and Random models.

```{r}
phtest(model_fixed_internal,model_random_internal)
```

As we can see, in this case, Fixed Effects Model suits better.
